Bullet Groups as a test of $\Lambda$CDM

### 2014-03-06 paper/ms.tex
improving the first subsection

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

The panel with the physical displacements also shows a vertical stripe
with the estimated displacement for the Bullet-group reported by
\cite{Gastaldello}. Considering this system as consistent withe the
groups sample we see that a fraction of $\sim XX\pm XX\%$ of the groups
should present a displacement equal or larger than the one estimated
for \bullg. The panel with the normalized displacements shows a
distribution that can be considered close to universal in the sense
that the two samples (groups and clusters) at all redshifts present a
similar trend.[...]

Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
composed by the ratio of the two circular velocities $V_{\rm c,
  sub}/V_{\rm c, host}$ and the physical displacements. In each of the
halo samples (left, groups; right, clusters) the two-dimensional
distributions are similar and have been therefore integrated to build
the 2D histogram.

On top of these 2D histograms there is an circle with error bars that
represents the observational estimates for the system \bullg. [...]

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacements}}
\label{fig:velocities}
\end{figure*}

@@

@@

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
\end{center}
\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
for different z. The top panel is represented to the sample with $v > 700$ \kms and down panel is represented 
for $v<700$ \kms} 
\label{cos_theta1}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
\end{center}
\caption{Integrated distributions of $|\vec{v}|/V_{\rm c,host}$ at all
  $z$. The left panel correponds to the sample with $V_{\rm c, host}>700$ \kms and
  right panel correpond to the sample with $V_{\rm c,host}<700\kms$.} 
\label{cos_theta2}
\end{figure*}

@@

\subsection{Number expected of Bullet Groups in the sample}

In order to estimate the number of Bullet Groups expected in the
Bolshoi Cosmological Simulation, we define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
we make the scalar product between the velocity vector and position vector that defines the separation between 
 the host halo and the substructure, as shown below: \\

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_4_VcircsubVcirchalo_300kms_700kms.eps}
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

The panel with the physical displacements also shows a vertical stripe
with the estimated displacement for the Bullet-group reported by
\cite{Gastaldello}. Considering this system as consistent withe the
groups sample we see that a fraction of $\sim 15\pm 2\%$ of the groups
should present a displacement equal or larger than the one estimated
for \bullg, this fraction is close to $45\pm2\% $. The panel with the
normalized displacements shows a  distribution that can be considered
close to universal in the sense that the two samples (groups and
clusters) at all redshifts present a similar trend.[...]

Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
composed by the ratio of the two circular velocities $V_{\rm c,
  sub}/V_{\rm c, host}$ and the physical displacements. This is
revealing because these two quantities can be constrained by
observations. The displacement is a direct observable, while the ratio
of the circular velocities can be estimated from lensing studies or
approximated by the ratio of the total galaxy luminosity associated
with the galaxy peaks.

To construct this figure we co-add all the halos in the sample (left,
groups; right, clusters) at all redshifts. We stack the data because
we do not observe any strong time evolution, aditionally this allows
us to increase the signal in each bin. Overplotted there is an circle
with error bars that represents the observational estimates for the
system \bullg.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacements}}
\label{fig:velocities}
\end{figure}

@@

The panel with the normalized velocities shows that the distribution
of sub-halo velocities is close to universal. Regardless
of the mass of the host halo and the redshift the integrated
distributions lie very close to each other.

The median of this distribution is located at $v/V_{\rm
  c,host}=1.1$. We also note the strong break at $v/V_{\rm
  c,host}=3.0$ that is present in the data from the group sample that
allows us to probe fractions on the order of $10^{-4}$.  This break is
located close the escape velocity of $v/V_{\rm c,host}$ for dark
matter halos following a NFW profile with a concentration value
$c\approx 6$ \citep{Hayashi2006}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
\end{center}
\caption{x}
\label{fig:velocities}
\end{figure*}

@@

@@
